---
title: "flexdashboard Project R"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(shiny)
library(ggplot2)
library(gganimate)
library(gifski)
library(shinythemes)

# Importing and preparing data

dat <- read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1"))
data <- read_csv(url("https://www.dropbox.com/s/uhfstf6g36ghxwp/cces_sample_coursera.csv?raw=1"))

dat$Party<-recode(dat$dem,`1`="Democrat",`0`="Republican")
```

Scatterplot with smoothing {data-orientation=rows}
===================================================

### Passage and Vote Relationship - Scatterplot with smoothing

```{r}
ggplotly( # Creating an interactive plot
  dat %>% # Selecting dataset
  drop_na() %>% # Dropping NA values
  filter(congress==110) %>% # Selecting only data for 110th Congress
  ggplot(
   aes(x=votepct, y=all_pass, color=Party))+ # Selecting x and y axis and filling
   geom_jitter()+ # Making scatterplot
   geom_smooth()+ # Adding smoothing
   scale_color_manual(values=c("#013274", "#bd0d22"))+ # Selecting colors 
   labs(x="Vote Pct.", y="Al Pass", title="Passage and Vote Pct., 110th Congress") # Adding labels
)
```

### Passage and Ideology Relationship - Scatterplot with smoothing 

```{r}
ggplotly( 
  dat %>%
  drop_na() %>%
  filter(congress==110) %>%
  ggplot(
    aes(x=dwnom1, y=all_pass, color=Party))+
    geom_point()+
    geom_smooth()+
    scale_color_manual(values=c("#013274", "#bd0d22"))+
    labs(x="DW Nominate.", y="All Pass", title="Passage and Ideology, 110th Congress")
)
```

Interactive filtering
======================

```{r}
# Preparing data for the graph
dat2 <- dat %>% 
  group_by(st_name) %>% # Grouping - needed for summarising data
  filter(congress==110) %>%
  summarise(passed=sum(all_pass)) # Summarizing by sum of passes
```

Input{.sidebar} 
---------------------
```{r}
# Creating sidebar - interactive filter to be used by user
selectInput(inputId = "st_name",
            label = "State",
            choices = unique(dat2$st_name), # All states can be selected by a user
            selected = unique(dat2$st_name), # By default all states are selected
            multiple = TRUE) # Multiple states may be selected
```

Column 
-------------------

### Total bills passed by state - interactive bar chart

```{r}
renderPlotly( # Creating an interactive graph
  ggplot(
   filter(dat2, st_name==input$st_name), # By default, all states are chosen 
   aes(x=st_name, y=passed, fill=passed))+
   geom_bar(stat="identity",text=NULL, fill="#013274")+ # Creating a bar chart, y values are provided
   coord_flip()+ # Creating a horizontal graph
   labs(x="State Name", y="Total Bills Passed per State", title="Total Bills by State Delegations, 110th Congress")+
   theme(legend.position="none") # Removing legend
   )
```

2 Tabs with interactive filter
===============================

```{r}
# Preparing data
data <- data %>% 
  drop_na() %>%
  select(c("pid7","ideo5","newsint","gender","educ","CC18_308a","region")) # Selecting needed columns
```

Input{.sidebar} 
---------------------
```{r}
# Creating sidebar - interactive filter to be used by user
sliderInput(inputId="ideo5", 
            label = "Select Five Point Ideology (1=Very liberal, 5=Very conservative)",
            min = 1, 
            max = 5,
            value = 3) # Default value selected
```

Column{.tabset}
------------------------

### Count of questioned by idelogy and political beliefs

```{r}
renderPlotly(
  ggplot(
    filter(data, ideo5==input$ideo5), # Ideology can be selected by user
    aes(x=pid7))+
    geom_bar(fill="#013274")+
    labs(x="7 Point Party ID, 1=Very D, 7=Very R")
)
```

### Count of questioned by ideology and Trump support 

```{r}
renderPlotly(
  ggplot(
    filter(data, ideo5==input$ideo5), 
    aes(x=CC18_308a))+
    geom_bar(fill="#bd0d22")+
    labs(x="Trump Support")
)
```

Scatterplot and boxplot {data-orientation=rows}
=========

### Bills passed by gender - faceted scatter plot

```{r}
# Filtering data for the graph
filtered <- filter(dat, congress==115)
filtered$majority <- recode(filtered$majority, `0`="Minority", `1`="Majority")
Gender <- recode(filtered$female,`0` = "male", `1` = "female")
```

```{r}
ggplot(
  filtered, 
  aes(x=votepct, y=all_pass, color=Gender))+
  geom_point()+
  scale_color_manual(values=c("#bd0d22", "#013274"))+
  labs(x="Vote Percentate", y="Bills Passed")+
  facet_wrap(~majority) # Creating two separate graphs per majority
```

### Legislative effectiveness - boxplot

```{r}
# Filtering data for the graph
filtered <- filter(dat, congress==115)
filtered$majority <- recode(filtered$majority, `0`="Minority", `1`="Majority")
```

```{r}
ggplot(
  filtered, 
  aes(y=les, x=majority, group=majority, fill=majority))+
  geom_boxplot()+
  labs(x="Majority or Minority", y="Legislative Effectiveness", title="LES in the 115th Congress", fill=dat$majority)+
  scale_fill_manual(values=c("#bd0d22", "#013274"))
```

Animations {data-orientation=rows}
===================================

### Animation by city - random data

```{r}
# Creating data for animation (code in this chunk was predefined by course instructor)
Category<-c("Alpha","Beta","Zeta")
City<-c("Hong Kong","London","Nairobi")

my_dat<-expand_grid(Category,City)
set.seed(84684)
my_dat$Value<-sample(1:10,9,replace=T)
```

```{r problem_1_solution,echo=FALSE,message=FALSE}
animate( # Creating an animation
  ggplot(
   my_dat, 
   aes(x=Category, y=Value, fill=City))+ # Choosing data, axis data and filling
   geom_bar(stat="identity")+ 
   transition_states(City)+ # Transition performed by city
   scale_fill_manual(values=c("#bd0d22", "#8db046", "#013274"))+ 
   enter_fade()+ # Adding enter fade
   exit_fade() # Adding exit fade
)
```

### Animated lollipop chart - random data

```{r}
# Creating data for a graph (code in this chunk was predefined by course instructor)
Category<-seq(from=1,to=10)
Time<-seq(from=1,to=10)

dat3<-expand_grid(Category,Time)
set.seed(78957)
dat3$Quantity<-runif(100,0,10)
```

```{r}
ggplotly( # Creating an interactive animation
  ggplot(
    dat3, 
    aes(x=Category, y=Quantity, frame=Time))+
    geom_point(color="#013274")+ # Adding points to the graph
    geom_segment(aes(x=Category, xend=Category, y=0, yend=Quantity))+ # Adding stems to the graph
    theme(axis.text.x=element_text(angle=90)) # Rotating labels on x axis
)
```

# Copyright notice

This project is a collection of graphics created for Coursera specialization [Data Visualization & Dashboarding with R.](https://www.coursera.org/specializations/jhu-data-visualization-dashboarding-with-r) 

Publically available data were used ([link 1](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/WOT7O8), [ link 2](https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1), [ link 3](https://www.dropbox.com/s/uhfstf6g36ghxwp/cces_sample_coursera.csv?raw=1)) and were used exclusively for educational purposes. 

Kinga Siwiec, 2021
